\textsc{Regression And Resampling Techniques \\ FYS-STK4155 \\ Assignment One}

### 2019-09-16 assignment_one/article/main.tex
Working on confidence intervals

\newcommand{\x}{\bm{x}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\X}{\bm{X}}
\newcommand{\diag}[1]{\mathrm{diag}(#1)}
\newcommand{\MSE}[1]{\mathrm{MSE}(#1)}
\newcommand{\R}[1]{\mathrm{R}^2(#1)}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\OLS}{\mathrm{OLS}}
\newcommand{\ridge}{\mathrm{ridge}}
\newcommand{\lasso}{\mathrm{lasso}}
\newcommand{\python}{\textsf{Python}{}}
\newcommand{\sgn}{\,\mathrm{sign}{}}

@@

  For the real data set, we use the supplied \textsc{Tiff} data of an area
  close to Stavanger in Norway, as displayed in \cref{fig:terrain}. The
  data-set consists of approximately \( 1800 \times 3600 \) data-points. 
  \begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{images/terrain.pdf}
    \caption{Real terrain data from a region close to Stavanger, Norway. For
    the regression tasks, we select data from small rectangular regions to keep
  the data-sizes manageable. The data is supplied in the file
\texttt{SRTM\_data\_1\_Norway.tif}.}
  \label{fig:terrain}
  \end{figure}

@@

>>>>

\newcommand{\x}{\bm{x}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\X}{\bm{X}}
\newcommand{\diag}[1]{\mathrm{diag}(#1)}
\newcommand{\MSE}[1]{\mathrm{MSE}(#1)}
\newcommand{\R}[1]{\mathrm{R}^2(#1)}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\var}{\mathbb{V}}
\newcommand{\cov}{\mathrm{Cov}}
\newcommand{\OLS}{\mathrm{OLS}}
\newcommand{\SD}{\mathrm{SD}}
\newcommand{\ridge}{\mathrm{ridge}}
\newcommand{\lasso}{\mathrm{lasso}}
\newcommand{\python}{\textsf{Python}{}}
\newcommand{\sgn}{\,\mathrm{sign}{}}

@@

  For the real data set, we use the supplied \textsc{Tiff} data of an area
  close to Stavanger in Norway, as displayed in \cref{fig:terrain}. The
  data-set consists of approximately \( 1800 \times 3600 \) data-points. 
  \begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{images/terrain.png}
    \caption{Real terrain data from a region close to Stavanger, Norway. For
    the regression tasks, we select data from small rectangular regions to keep
    the data-sizes manageable. The data is supplied in the file
    \texttt{SRTM\_data\_1\_Norway.tif}.}
  \label{fig:terrain}
  \end{figure}

@@

  \section{Model statistics and resampling methods}

  We are interested in computing certain statistical quantities pertaining to
  our data and corresponding model function. Firstly, the \emph{variance} of
  the model parameters \( \beta \) over all possible data sets tells us how
  sensitive \( \beta \) is to changes in the sampled data set. Using
  \cref{eq:optimal} for the optimal OLS-parameters and setting \( \mat{A} =
  (\X^T\X)^{-1}\X^T\), we compute:
  \begin{align}
	  \label{eq:ols_variance}
	  \cov\left[\beta_{\OLS}\right] &= \cov\left[\mat{A}\y\right] = \mat{A} \cov\left[\y\right] \mat{A}^T = \mat{A}\mat{A}^T\sigma^2 = (\X^T{\X})^{-1} \sigma^2.
  \end{align}
  In this calculation, we have used \cref{as:general_linear} to deduce that \(
  \cov[ \y ] = \diag{\sigma}\), a diagonal matrix, which commutes with other
  matrices. It then follows that the estimated variance of \( \beta_{\OLS} \) is given by
  \begin{equation}
	  \var[\beta_{\OLS}] = [\sigma^2 (\X^T\X)^{-1}_{ii} ]_{i=1}^n.
  \end{equation}
  Furthermore, by direct computation, we see that \( \beta_{\OLS} \) is an \emph{unbiased} estimator,
  as 
  \begin{equation}
	  \expect[\bias_{\OLS}] = \beta.
  \end{equation}
  With both the expected value and the variance of \( \beta \), we may
  formulate a confidence interval for \( \beta \). Thus for an estimated
  parameter \( \beta_i \) we construct the
  \(95\%\)-confidence interval as
  \begin{align}
	  \begin{split}
		  I_i &= (\expect[\beta_i] - 1.96 \times \SD[\beta_i], \expect[\beta_i] + 1.96 \times \SD[\beta_i]) \\
		      &= \left(\beta_i - 1.96 \times \sigma \sqrt{(\X^T\X)^{-1}_{ii}}, \beta_i + 1.96 \times \sigma \sqrt{(\X^T\X)^{-1}_{ii}}\right).
	  \end{split}
  \end{align}
  Here \( \SD[\beta_i] \) denotes the standard deviation of \( \beta_i \).  The
  interpretation of this interval is  ``under repeated experiments, the number
  of computed confidence intervals that actually include the true parameter,
  will tend to \( 95\% \)''.
